Size-differentiated Export in different Dynamical Regimes in the Ocean

### 2019-03-03 size_differentiated_export.tex
Updates from Overleaf

% FIG2
\begin{figure}[t]
	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}
	\caption{PSOM configuration for \textit{Papa\_summer}. (a) Time series of net heat fluxes and wind stress prescribed at the surface. Notice the positive heat fluxes, as well as downfront winds (i.e. eastward) persisting throughout the experiment. (b)-(d) horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in June and July are superimposed (dashed lines), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_summer}
\end{figure}

@@

% FIG3
\begin{figure}[ht]
	\includegraphics[width = 1\linewidth]{figures/Fig3_Papa500_winter}
	\caption{PSOM configuration for \textit{Papa\_winter}. (a) time series of net heat fluxes and wind stress prescribed at the surface. Notice the mostly negative heat fluxes, as well as alternating zonal wind direction. (b)-(d) horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 0, 30, and 50. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 0, 30, 50, and 80, showing the persistence of the halocline between z = 80 and z =180 m throughout the experiment (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in March is superimposed (dashed line), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_winter}
\end{figure}

@@

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles, is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\% of total export). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}).

\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
%The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).

%FIG6
\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	\caption{Upward (top) and downward (bottom) fluxes of particles at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are  For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\label{fig: particle_export}
\end{figure}

Time series of exported particles in \textit{Papa\_winter} present major differences. In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking. This earlier arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation. Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}. About 5\% of particles sinking at 0.025 m/day are exported. However, particle export is now stretched over longer periods of time due to particle resuspension. This can be seen in the gentler slopes of the export curves observed in \textit{Papa\_winter} than in \textit{Papa\_summer}.

@@

The presence of submesoscale dynamics therefore increases the number of exported slow-sinking simulated particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass per particle (Figure \ref{fig: sinking_velocity_spectrum}). While the percentage of exported particles is a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the number of particles exported when submesoscales features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.

>>>>

% FIG2
\begin{figure}[t]
	\includegraphics[width = 1\linewidth]{figures/Fig2_Papa500_summer}
	\caption{PSOM configuration for \textit{Papa\_summer}. (a) Time series of net heat fluxes and wind stress prescribed at the surface. Notice the positive heat fluxes, as well as downfront winds (i.e. eastward) persisting throughout the experiment. (b)-(d) surface horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 105, 135, and 165. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 105, 135, 165, and 195, showing the development of summer stratification centered at z = 30 m (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in June and July are superimposed (dashed lines), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_summer}
\end{figure}

@@

% FIG3
\begin{figure}[ht]
	\includegraphics[width = 1\linewidth]{figures/Fig3_Papa500_winter}
	\caption{PSOM configuration for \textit{Papa\_winter}. (a) time series of net heat fluxes and wind stress prescribed at the surface. Notice the mostly negative heat fluxes, as well as alternating zonal wind direction. (b)-(d) surface horizontal buoyancy gradients $M^2 = |\nabla_Hb|^2$ (in s$^{-2}$) at day of year (doy) 0, 30, and 50. Black contours show isopycnals (in kg/m$^3$; CI = 0.01 kg/m$^3$). (e) Vertical profile of the buoyancy frequency $N^2$ at doy 0, 30, 50, and 80, showing the persistence of the halocline between z = 80 and z =180 m throughout the experiment (solid lines). Monthly-average vertical stratification obtained from glider profiles collected in March is superimposed (dashed line), along with the correlation coefficient between observations and model outputs.}
	\label{fig: Papa_winter}
\end{figure}

@@

The domain-integrated flux of simulated particles crossing the 100 m export horizon, normalized by the total number of particles in each class (N = 1,971,717), is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions than slower-sinking particles. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking (Figure \ref{fig: particle_export}a). The particle flux is therefore exclusively downward, as the sinking rate of the particles in these sinking-velocity classes are larger than the advective sinking velocity ($w_s > w_{flow}$; see Figure \ref{fig: dynamics}).

%\fixme{mention deviations from dashed line. Mention resuspension (less than 1\%) for slow-sinking particles only due to vertical velocities.}
%The percentage of simulated particles crossing the 100 m export horizon with time is shown in Figure \ref{fig: particle_export} for both \textit{Papa\_summer} and \textit{Papa\_winter}. As expected, the faster-sinking particles are exported earlier and in larger proportions. For \textit{Papa\_summer} specifically, only the two fastest sinking-velocity classes (5 and 1 m/day) are exported within the first 28 days after seeding, while the other sinking-velocity classes do not significantly export particles over this time period ($<$ 5\%). In fact, time series of exported particles closely follow the curves derived from considering only gravitational sinking only (Figure \ref{fig: particle_export}).

%FIG6
\begin{figure}[ht]
	\centering
	\includegraphics[width = 1\linewidth]{figures/Fig6_particle_export_flux.png}
	\caption{Upward (top) and downward (bottom) fluxes of particles (thin lines) at the 100 m depth horizon as a function of time in \textit{Papa\_summer} (left), and \textit{Papa\_winter} (right). Fluxes are normalized by the total amount of particles (N = 1,971,717), daily-averaged and integrated over the entire domain. For each sinking-velocity class, the net particle flux is shown by a thick line. Expected downward fluxes based on only gravitational sinking are indicated with dashed lines in the left panels.}
	\label{fig: particle_export}
\end{figure}

Time series of particle fluxes in \textit{Papa\_winter} present major differences. In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking. This hastened arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation. Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}. About 5\% of particles sinking at 0.025 m/day are exported within the first 28 days of the experiment. However, particle export is now stretched over longer periods of time due to particle resuspension. In fact, the upward flux of particles in \textit{Papa\_winter} tends to mirror the measured downward flux (Figure \ref{fig: particle_export}b), exhibiting similar features, such as the sudden increase in particle flux occurring at day 68 due to a wind impulse generating internal waves (see Figure \ref{fig: Papa_winter}a). These similarities suggest that advecting processes leading to an export flux are mostly reversible (e.g., internal waves, cyclo-geostrophy due to meandering jet). However, the net particle fluxes for all sinking-velocity classes remain generally downward, suggesting that some irreversible mechanisms are also occurring at submesoscales.

%Time series of exported particles in \textit{Papa\_winter} present major differences. In every sinking-velocity class, particles reach the export depth faster than expected from gravitational sinking. This earlier arrival of particles is accentuated as the sinking-velocity decreases, ranging from about 1 day early for particles sinking at 5 m/day, to about 10 days early for particles sinking at a rate of 1 m/day. Sinking-velocity classes that are not expected to reach the export depth within the first 28 days now significantly contribute to export within the first 15 days of the simulation. Over 20\% of particles sinking at 0.5 m/day is now exported, versus less than 5\% in \textit{Papa\_summer}. About 5\% of particles sinking at 0.025 m/day are exported. However, particle export is now stretched over longer periods of time due to particle resuspension. This can be seen in the gentler slopes of the export curves observed in \textit{Papa\_winter} than in \textit{Papa\_summer}.

@@

The presence of submesoscale dynamics therefore hastens particle export, and increases the number of exported slow-sinking particles, by anywhere between a few percent and tens of percents, depending on the sinking-velocity class. This has large implications on the amount of biomass exported, as slower-sinking particles are far more numerous than faster-sinking particles, despite containing less biomass per particle (Figure \ref{fig: sinking_velocity_spectrum}). While the normalized particle flux is solely a function of the flow field, the exported biomass also depends on the Junge slope (see Equation (\ref{eq: biomassjungeslope})).

The impact of ocean dynamics on the respective contributions of the different sinking velocity classes to the total exported biomass is fairly intuitive: For a specific Junge slope, the presence of submesoscale dynamics enhances the role played by slower-sinking particles in biomass export and decreases the importance of faster-sinking particles (dashed lines in Figure \ref{fig: biomass_export_remin}). This is a logical result given the observed increase in the particle export flux when submesoscales features are present (Figure \ref{fig: particle_export}). The sinking class dominating export, however, is highly dependent on the Junge slope. As the Junge slope increases, the particle spectrum steepens, and the contribution of slower-sinking particles to the total exported biomass increases. For example, after 28 days, the 1 m/day particle class exports 50\%, 100\%, and 125\% of the biomass exported by the 5 m/day class when $\xi =$ 2, 3, and 4, respectively.
